---
title: "Exercise Sheet 3"
author: "Andrej Dragic (12803423)"
date: "2025-06-03"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise 1: Initializing git

### 1d) Two strengths and two weaknesses of git

**Strengths:**
- Enables version control and team collaboration.
- Allows easy rollback to previous versions.

**Weaknesses:**
- Merge conflicts can be complex for beginners.
- Requires basic command line knowledge.

## Exercise 2: Putting your Repository on GitHub

GitHub Repository:  
[https://github.com/drejan-ns/exeRcise-sheet-3](https://github.com/drejan-ns/exeRcise-sheet-3)

## Exercise 3: Pixar Films

### Part 3a: Load and clean pixar_films dataset

```{r}
pixar <- read.csv("pixar_films.csv")
pixar_clean <- subset(pixar, film != "")
pixar_clean$film_rating <- factor(pixar_clean$film_rating)
unique(pixar_clean$film_rating)
table(pixar_clean$film_rating)
```

The possible values for `film_rating` are:
- **G** (General Audience): Suitable for all ages.
- **PG** (Parental Guidance): Some material may not be suitable for children.
- **NA**: Rating is not available or missing.

Converting `film_rating` to a factor is appropriate because it is a categorical variable with a fixed set of possible values. Treating it as a factor allows R to handle it correctly in summaries, plots, and statistical models.


### Part 3b: Identify film series and count entries

We manually inspected the titles and assigned films to series based on shared keywords.

```{r}
pixar_clean$series <- NA
pixar_clean$series[grepl("Toy Story", pixar_clean$film)] <- "Toy Story"
pixar_clean$series[grepl("Cars", pixar_clean$film)] <- "Cars"
pixar_clean$series[grepl("Finding", pixar_clean$film)] <- "Finding"
pixar_clean$series[grepl("Monsters", pixar_clean$film)] <- "Monsters"
pixar_clean$series[grepl("Incredibles", pixar_clean$film)] <- "Incredibles"

library(dplyr)

series_summary <- pixar_clean %>%
  filter(!is.na(series)) %>%
  group_by(series) %>%
  summarise(
    titles = paste(film, collapse = ", "),
    count = n()
  )

series_summary
```


### Part 3c: Load public_response and merge with pixar_clean

We load the dataset, convert `cinema_score` to an ordered factor, and merge it with the main dataset.

```{r}
public_response <- read.csv("public_response.csv")

# inspect unique values
unique(public_response$cinema_score)

# convert to ordered factor
public_response$cinema_score <- factor(
  public_response$cinema_score,
  levels = c("A-", "A", "A+"),
  ordered = TRUE
)

# merge datasets
combined <- merge(pixar_clean, public_response, by = "film")

```


### Part 3d) Create a bar plot of public response by film series

We plot Rotten Tomatoes scores for all Pixar films that belong to a series.

```{r}
library(ggplot2)

ggplot(
  data = combined[!is.na(combined$series), ],
  aes(x = series, y = rotten_tomatoes, fill = film)
) +
  geom_bar(stat = "identity", position = position_dodge()) +
  labs(
    title = "Rotten Tomatoes Scores of Pixar Film Series",
    x = "Film Series",
    y = "Rotten Tomatoes Score",
    fill = "Film Title"
  ) +
  theme_minimal()
```

The plot shows that within a series, the first film often receives the highest score (e.g. Toy Story, Cars). In some cases (like Finding Dory), the sequel maintains similar quality. The drop in scores across sequels may reflect audience fatigue or lower innovation.

