---
title: "Exercise Sheet 3"
author: "Andrej Dragic (12803423)"
date: "2025-06-03"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise 1: Initializing git

### 1d) Two strengths and two weaknesses of git

**Strengths:**
- Enables version control and team collaboration.
- Allows easy rollback to previous versions.

**Weaknesses:**
- Merge conflicts can be complex for beginners.
- Requires basic command line knowledge.

## Exercise 2: Putting your Repository on GitHub

GitHub Repository:  
[https://github.com/drejan-ns/exeRcise-sheet-3](https://github.com/drejan-ns/exeRcise-sheet-3)

## Exercise 3: Pixar Films

### Part 3a: Load and clean pixar_films dataset

```{r}
pixar <- read.csv("pixar_films.csv")
pixar_clean <- subset(pixar, film != "")
pixar_clean$film_rating <- factor(pixar_clean$film_rating)
unique(pixar_clean$film_rating)
table(pixar_clean$film_rating)
```

The possible values for `film_rating` are:
- **G** (General Audience): Suitable for all ages.
- **PG** (Parental Guidance): Some material may not be suitable for children.
- **NA**: Rating is not available or missing.

Converting `film_rating` to a factor is appropriate because it is a categorical variable with a fixed set of possible values. Treating it as a factor allows R to handle it correctly in summaries, plots, and statistical models.


